%-------------------------
% Backend Agentic AI Engineer Resume (ATS Optimized)
%-------------------------

\documentclass[letterpaper,11pt]{article}

% Packages
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{enumitem}
\usepackage[dvipsnames]{xcolor}
\input{glyphtounicode}

% Header/Footer
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.2in}

% Section formatting
\titleformat{\section}
{\vspace{-4pt}\color{BrickRed}\scshape\large\bfseries}
{}{0em}{}[\color{BrickRed}\titlerule \vspace{-6pt}]

% Commands
\newcommand{\resumeItem}[1]{\item\small{{#1}}}

\newcommand{\resumeSubheading}[4]{
\vspace{-3pt}\item
\begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{#1} & \textbf{\small #2} \\
\textit{\small #3} & \textit{\small #4} \\
\end{tabular*}
\vspace{-6pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in,label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}} 
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in,itemsep=2pt]} 
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%---------- HEADER ----------
\begin{center}
{\Huge \scshape Saurabh Prashant Gathade} \\ \vspace{4pt}
\small
\faPhone~ +91 9689525960 ~·~
\href{mailto:saurabhgathade@gmail.com}{\faEnvelope~ saurabhgathade@gmail.com} ~·~
\href{https://www.linkedin.com/in/saurabhpgathade}{\faLinkedin~ LinkedIn} ~·~
\href{https://github.com/Saurabhgathade131}{\faGithub~ GitHub}
\end{center}

%---------- SUMMARY ----------
\section{Summary}
\small Backend \& Agentic AI Engineer with 3+ years of experience building scalable backend systems and designing \textbf{multi-agent AI architectures} for enterprise automation. Expertise in \textbf{agentic workflows}, \textbf{AI agent orchestration}, \textbf{multi-agent systems}, \textbf{tool-use patterns}, and \textbf{autonomous decision pipelines}. Proficient in \textbf{FastAPI}, \textbf{Node.js}, \textbf{Microsoft Agent Framework}, \textbf{Rovo Agents}, \textbf{Redis}, \textbf{MongoDB}, and \textbf{cloud-native deployments} on AWS/GCP. Focused on building production-grade agentic systems with observability, reliability, and scalability.

%---------- SKILLS ----------
\section{Technical Skills}
\resumeSubHeadingListStart
\item\small{
\textbf{Agentic AI:} Multi-Agent Systems, Agent Orchestration, Agentic Workflows, Tool-Use Patterns, Autonomous Decision Pipelines \\
\textbf{AI Frameworks:} Microsoft Agent Framework (.NET), Rovo Agent Framework, LLM Integration, Prompt Engineering \\
\textbf{Backend:} Node.js, Express.js, FastAPI, REST APIs, GraphQL, Microservices, Serverless \\
\textbf{Databases:} MongoDB, PostgreSQL, Redis, DynamoDB (basic) \\
\textbf{Realtime:} WebSockets, Socket.IO, Redis Pub/Sub, GraphQL Subscriptions \\
\textbf{Cloud:} AWS (Lambda, EC2, S3, API Gateway), GCP (Cloud Run, Pub/Sub) \\
\textbf{DevOps:} Docker, CI/CD, GitHub Actions, Nginx, Serverless Framework \\
\textbf{Frontend:} React.js, Next.js, Redux Toolkit, TailwindCSS, React Native \\
\textbf{Other:} Design Patterns (Decorator, Strategy), SOLID Principles, Canonical Logging, Observability, API Security
}
\resumeSubHeadingListEnd
\vspace{-10pt}

%---------- EXPERIENCE ----------
\section{Work Experience}
\resumeSubHeadingListStart

% Qualizeal
\resumeSubheading{Qualizeal}{Dec 2025 -- Present}{Full Stack \& AI Engineer}{Hyderabad}
\resumeItemListStart
\resumeItem{Architected and delivered an \textbf{AI-driven framework migration system} enabling automated conversion of test automation projects using \textbf{FastAPI}, \textbf{LLM-powered multi-agent orchestration}, and autonomous code transformation pipelines, reducing manual effort by \textbf{60\%+}.}
\resumeItem{Designed and implemented \textbf{end-to-end agentic AI architecture} for code transformation, validation, and execution workflows with scalable, modular \textbf{inter-agent communication protocols}.}
\resumeItem{Architected an \textbf{AI-driven framework migration system} across frameworks using \textbf{FastAPI} and multi-agent orchestration, reducing manual effort by \textbf{60\%+}.}
\resumeItem{Designed \textbf{end-to-end AI agent architecture} for code transformation, validation, and execution workflows.}
\resumeItem{Led development of a \textbf{Test Automation Agentic Workflow} with specialized agents: \textbf{UI Explorer Agent}, \textbf{Code Generator Agent}, and \textbf{Code Analysis Agent}.}
\resumeItem{Engineered agent workflows using \textbf{Microsoft Agent Framework (.NET)} for intelligent decision pipelines.}
\resumeItem{Implemented \textbf{Decorator Pattern-based logging framework} with canonical logging, improving observability across distributed systems.}
\resumeItem{Applied \textbf{SOLID principles and DRY architecture} to design scalable, production-grade systems.}
\resumeItemListEnd

% Techolution
\resumeSubheading{Techolution}{Apr 2024 -- Dec 2025}{Full Stack Engineer}{Remote}
\resumeItemListStart
\resumeItem{Engineered high-performance backend modules using \textbf{Node.js}, \textbf{Express}, and \textbf{MongoDB} supporting \textbf{AI agent orchestration} and distributed workflows.}
\resumeItem{Introduced \textbf{Redis Pub/Sub} pipelines for efficient real-time communication and low-latency event processing.}
\resumeItem{Crafted \textbf{FastAPI microservices} handling audio streaming, transcription, and model execution.}
\resumeItem{Refined \textbf{MongoDB schemas} for agents, configuration systems, and AI execution traces.}
\resumeItem{Created internal \textbf{NPM libraries} and automation tools accelerating development by \textbf{40\%}.}
\resumeItemListEnd

% I AM First Digition
\resumeSubheading{I AM First Digition Solutions Pvt. Ltd.}{Feb 2023 -- Mar 2024}{Full Stack Developer}{Nagpur}
\resumeItemListStart
\resumeItem{Implemented full-stack modules using \textbf{React}, \textbf{Node.js}, and \textbf{MongoDB} for production ed-tech systems.}
\resumeItem{\textbf{Contributed to JaiBhimConnect} mobile features using \textbf{React Native} and backend modules with \textbf{Node.js}.}
\resumeItemListEnd

% BYJU'S
\resumeSubheading{Think and Learn Pvt Ltd (BYJU'S)}{Oct 2020 -- Feb 2023}{Sr. Business Development Associate}{Ahmedabad}
\resumeItemListStart
\resumeItem{Ranked among the top 5 nationally; led sales initiatives and associate performance optimization.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%---------- PROJECTS ----------
\section{Projects}
\resumeSubHeadingListStart

\resumeSubheading{AI-Native Coding Interview Platform}{2025}{Agentic AI Project}{Next.js 14 · FastAPI · Azure OpenAI · Judge0 · Socket.io}
\resumeItemListStart
\resumeItem{Developed a professional AI-native interview platform using \textbf{Next.js 14}, \textbf{FastAPI}, and \textbf{Socket.io} for real-time interaction.}
\resumeItem{Integrated \textbf{Azure OpenAI} for an intelligent interviewer with \textbf{stuck detection}, contextual hinting, and natural language feedback.}
\resumeItem{Implemented secure live code execution and automated test validation via \textbf{Judge0 API} with \textbf{Monaco Editor} integration.}
\resumeItem{Built proctoring features including \textbf{tab-switch tracking} and \textbf{paste detection} to maintain interview integrity.}
\resumeItemListEnd

\resumeSubheading{Discipline Engine: Learning Command Center}{2025}{Full Stack Project}{React · TypeScript · AWS Lambda · DynamoDB · Serverless}
\resumeItemListStart
\resumeItem{Designed and deployed a full-stack learning progress tracker with \textbf{React} frontend, \textbf{TypeScript} backend, and \textbf{DynamoDB} persistence.}
\resumeItem{Implemented interactive daily schedules with \textbf{automated skill validation} and consistency reporting using \textbf{Serverless Framework} on AWS.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%---------- EDUCATION ----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{KDK College of Engineering, Nagpur (RTMNU)}{2016 -- 2020}{B.Tech in Computer Technology}{CGPA: 8.0/10}
\resumeSubHeadingListEnd

%---------- CERTIFICATIONS ----------
\section{Certifications}
\small Coding Ninjas: Java · Data Structures · Frontend · Backend · React.js

\end{document}
